\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-17 manuscript.Rmd
Undated EFA table

```{r factordetails, include=FALSE}
#Preparing the EFA table
fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(2)
  #supress loadings
  loadings[abs(loadings) < abs(cut)] <- ""
  #get additional info
  add_info <- cbind(x$communality, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(across(where(is.numeric), round, 3))
}
efa.tab <- fa_table(fa.5F.3,.3)

variance <- fa.5F.3$Vaccounted %>% 
  as.data.frame()%>% 
  round(2)
library(data.table)
efa.table <- rbind(setDT(efa.tab), setDT(variance[2,]), fill=TRUE)
efa.table[26,1] <- "% of variance"

>>>>

```{r factordetails, include=FALSE}
#Preparing the EFA table
library(data.table)
fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(2)
  #supress loadings
  loadings[abs(loadings) < abs(cut)] <- ""
  #get additional info
  add_info <- cbind(x$communality, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings <- loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(across(where(is.numeric), round, 3)) %>% 
    as.data.frame()
  variance <- x$Vaccounted %>% 
  as.data.frame()%>% 
  round(2)
  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)

}

efa.table <- fa_table(fa.5F.3,.3) 
nr <- nrow(efa.table)
efa.table[nr, 1] <- "% of Variance"
